---
title: "Your Title here"
#subtitle: "A subtitle"
author:
  - "Lachlan Deer$^1$"
  - "John Snow$^2$"
  - "Humpty Dumpty$^2$"
institute:
   - $^1$Juans Casa
   - $^2$Tus Place
date: "Summer 2018"
output:
  beamer_presentation:
    latex_engine: xelatex
    theme: "sthlm"
    colortheme: "sthlm"
    fonttheme: "sthlm"
    slide_level: 2
    #keep_tex: TRUE
classoption: "progressbar"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

# a section

## Slide with Bullets

* Bullet 1
* Bullet 2
* Bullet 3
    * sub bullet

\alert{sthlm}

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
